AP/PA Tables ITHIM Global

### 2020-09-30 summary_tables_PA_AP.Rmd
Update description of CO2 emissions

1) Individual-level PM2.5 concentrations for baseline and scenarios
2) Individual-level CO2 for baseline and scenarios
3) Individual-level physical activity for baseline and scenarios

>>>>

1) Individual-level PM2.5 concentrations for baseline and scenarios
2) Overall CO2 emissions for baseline and scenarios
3) Individual-level physical activity for baseline and scenarios
